Flowchart of Current Algorithm

### 2009-02-04 docs/flowchart/flowchart.tex
moved correct_base so it occurs before advect_base_pressure.  results will change slightly

\item Should we eeplace {\bf Correct Base} with $\rho_0 = {\rm{\bf Avg}}(\rho)$ in 
plane-parallel and $\rho_0 = \rho_0 - {\rm{\bf Avg}}(\rho_0 - \rho)$ in spherical?
This eliminates the need for $\nabla\cdot\etarho$.

\item In {\bf Step 4} and {\bf Step 8}, should we move {\bf Correct Base} so it 
occurs immediately before {\bf Advect Base Pressure}?  Since the full
enthalpy advance ``feels'' the effects of the time-centered $\etarho$, we should
rely on a $\rho_0^{n+1}$ that also feels the effects.

>>>>

\item Should we replace {\bf Correct Base} with $\rho_0 = {\rm{\bf Avg}}(\rho)$ in 
plane-parallel and $\rho_0 = \rho_0 - {\rm{\bf Avg}}(\rho_0 - \rho)$ in spherical?
This eliminates the need for $\nabla\cdot\etarho$.
